### 2012-11-14 paper/isca40format/Fifo.tex
will be removing evict req

We already gave the ordering requirements between messages (Figure
\ref{ordering}), and which messages should not be blocked by other
messages (Figure \ref{blocking}). These are the minimum constraints to
ensure correctness and deadlock-freedom of the hierarchical coherence
protocols. Any practical implementation will restrict the ordering between
messages further, but they must ensure that the messages that should not be
blocked according to Figure \ref{blocking} are not blocked. In this
section, we will discuss several such implementations. Note that the
constraints in Figures \ref{ordering} are on messages for the same
address; messages for different addresses can be processed in any order. This
permits implementation of non-blocking caches using MSHRs.

@@

Request messages now have the format \Req{src}{dst}{addr}{fromState}{toState}.
A downgrade request for an address from a parent to a child contains the
directory state of the parent for the address just before the request was sent,
in addition to value of the state to downgrade to. Similarly an upgrade request
for an address from child to its parent should contain the state of the child
for the address just before the request was sent, in addition to the value of
the state to upgrade to.

@@

Response messages sent from a child to its parent can also avoid relying on the
point-to-point FIFO ordering in the network using a similar approach. Response
messages from the child to its parent will now have the format
\Req{src}{P}{addr}{fromState}{toState}. A response \Resp{c}{P}{a}{x}{y} is not
handled by the parent if $dir[c][a] > x$ until it receives another response
\Resp{c}{P}{a}{w}{z} where $z \le x$.

@@

The implementation described above avoids the need for sending \emph{ack}
messages to guarantee the required ordering, thus reducing the number of
messages as well as unblocking a cache line (for handling further requests)
without waiting for acks.

>>>>

%We already gave the ordering requirements between messages (Figure
%\ref{ordering}), and which messages should not be blocked by other
%messages (Figure \ref{blocking}). These are the minimum constraints to
%ensure correctness and deadlock-freedom of the hierarchical coherence
%protocols. Any practical implementation will restrict the ordering between
%messages further, but they must ensure that the messages that should not be
%blocked according to Figure \ref{blocking} are not blocked. In this
%section, we will discuss several such implementations. Note that the
%constraints in Figures \ref{ordering} are on messages for the same
%address; messages for different addresses can be processed in any order. This
%permits implementation of non-blocking caches using MSHRs.

In this section, we show how the constraints of figures \ref{blocking} and
\ref{ordering} can be implemented realistically.
%We already gave the ordering requirements between messages (Figure
%\ref{ordering}), and which messages should not be blocked by other
%messages (Figure \ref{blocking}). These are the minimum constraints to
%ensure correctness and deadlock-freedom of the hierarchical coherence
%protocols. Any practical implementation will restrict the ordering between
%messages further, but they must ensure that the messages that should not be
%blocked according to Figure \ref{blocking} are not blocked. In this
%section, we will discuss several such implementations. Note that the
%constraints in Figures \ref{ordering} are on messages for the same
%address; messages for different addresses can be processed in any order. This
%permits implementation of non-blocking caches using MSHRs.

@@

A downgrade request for an address from a parent to a child contains the
directory state of the parent for the address just before the request was sent,
in addition to value of the state to downgrade to. Similarly an upgrade request
for an address from child to its parent should contain the state of the child
for the address just before the request was sent, in addition to the value of
the state to upgrade to. Request messages have a $fromState$ tagged to it, and
thus have a new format \Req{src}{dst}{addr}{fromState}{toState}.

@@

Response messages sent from a child to its parent can also avoid relying on the
point-to-point FIFO ordering in the network using a similar approach. Response
messages from the child to its parent will also have a $fromState$ field with
the new format \Req{src}{P}{addr}{fromState}{toState}. A response
\Resp{c}{P}{a}{x}{y} is not handled by the parent if $dir[c][a] > x$ until it
receives another response \Resp{c}{P}{a}{w}{z} where $z \le x$.

@@

The implementation described above avoids the need for sending \emph{ack}
messages to guarantee the required ordering, thus reducing the number of
messages as well as unblocking a cache line (for handling further requests)
ithout waiting for acks.
